Stabilization-Free Virtual Element Methods

### 2023-02-01 reports/response.tex

\item \textsf{Lines 41-43; you should underline that the polynomial spaces onto which you project are based on a regular simplicial tessellation of the elements of the mesh.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. We have mentioned it.

\medskip

\item \textsf{Lines 50-51; when you define the function $\phi$, are you sure that the normal component of the trace is a polynomial only on the faces of $K$? Don't you also need this property to be valid on the faces of the simplicial tessellation of $K$?}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Base on $d$-dimensional polytope $K\in \mathcal T_h$ and its simplicial partition $\mathcal T_K$ of $K$, we define the following $H(\div)$-conforming finite element spaces in this paper:
% For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
\begin{align*}    
\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)&=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}\textrm{ for } k\geq2, \\
\boldsymbol{V}^{\mathrm{RT}}(K)&=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}, \\
\boldsymbol{V}_{k-1}^{\rm div}(K)&=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K): \div\boldsymbol{\phi}\in\mathbb P_{k-2}(K)\}\textrm{ for } k\geq2, \\
\boldsymbol{V}_{0}^{\rm div}(K)&=\{\boldsymbol{\phi}\in\boldsymbol{V}_{0}^{\mathrm{RT}}(K): \div\boldsymbol{\phi}\in\mathbb P_{0}(K)\},
\\
\mathbb{V}_{k-1}^{\rm div}(K)&=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k-1}(F) \textrm{ for each } F\in\mathcal F(K)\}.
\end{align*}
We compare these spaces for polytope $K$ and face $F\in\mathcal F(K)$ in the following table.
\begin{center}
\renewcommand\arraystretch{1.3}
\begin{tabular}[t]{|c|c|c|c|}
% \toprule
\hline
$\boldsymbol{\phi}$ & $\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)/\boldsymbol{V}^{\mathrm{RT}}(K)$ & $\boldsymbol{V}_{k-1}^{\rm div}(K)$ & $\mathbb{V}_{k-1}^{\rm div}(K)$  \\
\hline
% \midrule 
$(\div\boldsymbol{\phi})|_K$ & piecewise polynomial & polynomial & polynomial \\
\hline
$(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ & piecewise polynomial & piecewise polynomial & polynomial \\
\hline
% \bottomrule
\end{tabular}
\end{center}
We can see that both $(\div\boldsymbol{\phi})|_K$ and $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ are polynomials for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$.

To ensure the $L^2$ projection
$Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
for virtual element function $v\in V_k(K)$, we only require
$(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ to be a polynomial for each $(d-1)$-dimensional face $F$ of $K$. But $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_F$ can be a piecewise polynomial for interior face $F$ of the simplicial tessellation of $K$.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. We have recalled it.

\medskip

\item \textsf{Line 305; reference [21, Lemma 10] for the polynomial inverse inequality is not proper; in fact, the inverse estimate follows from standard polynomial inverse estimates on simplices (refer, e.g., to Verf{\"u}rth's book), the regularity of the element, and standard polynomial inverse estimates.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We add references \cite{Ciarlet1978,Verfuerth2013} in the revised manuscript.

@@

\medskip

\item \textsf{Line 305; reference [11, (2.18)] is also a standard scaled trace inequality (refer to any PDE textbook).}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We add reference \cite[Theorem 1.5.1.10]{Grisvard1985} in the revised manuscript.

@@

\medskip

\item \textsf{Line 308-309; you also use the definition of negative norm (which I cannot find), an integration by parts, and a Cauchy-Schwarz inequality.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We revise the first part of the proof of Lemma 3.12 as follows.

By the inverse inequality \cite{Ciarlet1978,Verfuerth2013} (see also \cite[Lemma 10]{Huang2020}),
$$
h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim  \|\div\boldsymbol{\phi}\|_{-1,K},
$$ 
where
$$
\|\div\boldsymbol{\phi}\|_{-1,K}=\sup_{v\in H_0^1(K)}\frac{(\div\boldsymbol{\phi}, v)_K}{|v|_{1,K}}=-\sup_{v\in H_0^1(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{|v|_{1,K}} \leq \|\boldsymbol{\phi}\|_{0,K}.
$$
Then we have
\begin{equation}\label{eq:20230201}  
h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
\end{equation}
For $F\in\mathcal F^{\partial}(\mathcal T_K)$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$, then apply the trace inequality \cite[Theorem 1.5.1.10]{Grisvard1985} (see also \cite[(2.18)]{BrennerSung2018}) and the inverse inequality to get
$$
h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \|\boldsymbol{\phi}\|_{0,T}+h_T|\boldsymbol{\phi}|_{1,T}\lesssim \|\boldsymbol{\phi}\|_{0,T}.
$$ 
This means
$$
\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
$$ 
Combining \eqref{eq:20230201}, the Cauchy-Schwarz inequality and the last inequality yields
$$
h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
$$

@@

\medskip

\item \textsf{Line 310; “other side” $-\!\!\!-\!\!\!-\!\!\!>$“lower bound”.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
It has been corrected.

@@

\medskip

\item \textsf{Lines 311-312; are you sure about the definition of $\phi_1$? What about the degrees of freedom on internal faces?}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We define $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)$ based on DoFs (3.1)-(3.3).
To be specific, $(\boldsymbol{\phi}_1\cdot\boldsymbol{n})|_{\partial K}=(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{\partial K}$, and all the DoFs (3.1)-(3.3) of $\boldsymbol{\phi}_1$ interior to $K$ equal to zero.

@@

\medskip

\item \textsf{Elaborate more the equivalence (3.26).}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We revise it as follows.

By the norm equivalence on each simplex $T\in\mathcal T_K$ and the vanishing DoFs~(3.1)-(3.3), we get
\begin{align*}%\label{eq:20220324-5}
\|\boldsymbol{\phi}_1\|_{0,K}^2 = \sum_{T\in\mathcal T_K}\|\boldsymbol{\phi}_1\|_{0,T}^2 \eqsim \sum_{T\in\mathcal T_K}\sum_{F\in\mathcal F(T)}h_F\|\boldsymbol{\phi}_1\cdot\boldsymbol{n}\|_{0,F}^2 =\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2.
\end{align*}
Due to the vanishing DoF (3.2), it holds that $\div\boldsymbol{\phi}_1=Q_0^T(\div\boldsymbol{\phi}_1)$ for $T\in\mathcal T_K$.
Then apply the integration by parts and the Cauchy-Schwarz inequality to acquire
\begin{equation*}%\label{eq:202302011}  
\|\div\boldsymbol{\phi}_1\|_{0,T}^2=\|Q_0^T(\div\boldsymbol{\phi}_1)\|_{0,T}^2
\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap\mathcal F^{\partial}(\mathcal T_K)}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\;\;\forall~T\in\mathcal T_K.
\end{equation*}

@@

\medskip

\item \textsf{You should write that the eq. in 322 is proven based on the inequality on lines 315-316.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggest. We have revised it.

@@

\item \textsf{Line 149: “$(I +\boldsymbol{x}\cdot\nabla)\boldsymbol{w} = \boldsymbol{0}$, which implies $\boldsymbol{w} = \boldsymbol{0}$”. I do not see how this follows. We have that
$$(\nabla\boldsymbol{w}(\boldsymbol{x}))\boldsymbol{x}=-\boldsymbol{w}(\boldsymbol{x})\quad\forall\boldsymbol{x}\in T.
$$
It is not clear to me how the conclusion that $\boldsymbol{w} = \boldsymbol{0}$ follows. The authors
should precise their reasoning.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
...

\medskip

\item \textsf{In the proof of Lemma 3.12, the authors apply a discrete trace inequality to the
quantity 
$$
\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}
$$
and cite [11, (2.18)]. However, [11, (2.18)] is a continuous trace inequality and there is no justification given for why the discrete trace inequality holds in this particular case. Moreover, it is not explained how one concludes that $\|\div\boldsymbol{\phi}\|_{-1,K}\lesssim \|\boldsymbol{\phi}\|_{0,K}$.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
For $F\in\mathcal F^{\partial}(\mathcal T_K)$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$. We can use the trace inequality \cite[(2.18)]{BrennerSung2018} and the inverse inequality to get
$$
h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \|\boldsymbol{\phi}\|_{0,T}+h_T|\boldsymbol{\phi}|_{1,T}\lesssim \|\boldsymbol{\phi}\|_{0,T}.
$$ 
Then
$$
\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
$$

For the second question, it can be explained as follows:
$$
\|\div\boldsymbol{\phi}\|_{-1,K}=\sup_{v\in H_0^1(K)}\frac{(\div\boldsymbol{\phi}, v)_K}{|v|_{1,K}}=-\sup_{v\in H_0^1(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{|v|_{1,K}} \leq \|\boldsymbol{\phi}\|_{0,K}.
$$

### 2023-02-01 stabfreevem_sinum.tex
more revision

\subsection{Notation}
Let $\Omega\subset \mathbb{R}^d$ be a bounded
polytope. Given a bounded domain $K\subset\mathbb{R}^{d}$ and a
non-negative integer $m$, let $H^m(K)$ be the usual Sobolev space of functions
on $K$.
The corresponding norm and semi-norm are denoted respectively by
$\Vert\cdot\Vert_{m,K}$ and $|\cdot|_{m,K}$. By convention, let $L^2(K)=H^0(K)$. 
Let $(\cdot, \cdot)_K$ be the standard inner product on $L^2(K)$. If $K$ is $\Omega$, we abbreviate
$\Vert\cdot\Vert_{m,K}$, $|\cdot|_{m,K}$ and $(\cdot, \cdot)_K$ by $\Vert\cdot\Vert_{m}$, $|\cdot|_{m}$ and $(\cdot, \cdot)$,
respectively. Let $H_0^m(K)$ be the closure of $\mathcal C_{0}^{\infty}(K)$ with
respect to the norm $\Vert\cdot\Vert_{m,K}$, and $L_0^2(K)$ consist of all functions in $L^2(K)$ with zero mean value.
For integer $k\geq0$,
notation $\mathbb P_k(K)$ stands for the set of all
polynomials over $K$ with the total degree no more than $k$. Set $\mathbb P_{-1}(K)=\{0\}$.
For a banach space $B(K)$, let $B(K; \mathbb{X}):=B(K)\otimes\mathbb{X}$ with $\mathbb{X}=\mathbb{R}^d$ and $\mathbb{K}$, where $\mathbb{K}$ is the set of antisymmetric matrices.
Denote by $Q_k^{K}$ the $L^2$-orthogonal projector onto $\mathbb P_k(K)$ or $\mathbb P_{k}(K; \mathbb{X})$.
For tensor $\boldsymbol{\tau}$, let $\skw\boldsymbol{\tau}:=(\boldsymbol{\tau}-\boldsymbol{\tau}^{\intercal})/2$ be the antisymmetric part of $\boldsymbol{\tau}$.
Denote by $\#S$ the number of elements in a finite set $S$.

@@

In this section we will construct $H(\div)$-conforming macro finite elements in arbitrary dimension.
\subsection{$H(\div)$-conforming finite elements}
For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
\[
\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
\]
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x} \label{BDMdof3}
\end{align}
for $T\in\mathcal T_K$.
Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.

@@

\begin{lemma}\label{lem:Vkm1divnormequivalence}
For $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
\begin{equation}\label{eq:Vkm1divnormequivalence}
\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{equation}
\end{lemma}
\begin{proof}
By the inverse inequality \cite[Lemma 10]{Huang2020} and the trace inequality \cite[(2.18)]{BrennerSung2018}, we have
\begin{align*}
&\quad h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\\
&\lesssim \|\div\boldsymbol{\phi}\|_{-1,K} + \|\boldsymbol{\phi}\|_{0,K} \lesssim \|\boldsymbol{\phi}\|_{0,K}.    
\end{align*}

Next we focus on the proof of the other side. Again we only prove the case $k\geq2$, whose argument can be applied to case $k=1$. Take $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)$ such that $\boldsymbol{\phi}_1\cdot\boldsymbol{n}|_{\partial K}=\boldsymbol{\phi}\cdot\boldsymbol{n}_{\partial K}$, and all the DoFs \eqref{BDMdof1}-\eqref{BDMdof3} of $\boldsymbol{\phi}_1$ in the interior of $K$ vanish. We have
\begin{equation}\label{eq:20220324-5}
\|\boldsymbol{\phi}_1\|_{0,K}\eqsim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F},
\end{equation}
\[
\|\div\boldsymbol{\phi}_1\|_{0,T}^2=\|Q_0^T(\div\boldsymbol{\phi}_1)\|_{0,T}^2
\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap\mathcal F^{\partial}(\mathcal T_K)}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\quad\forall~T\in\mathcal T_K.
\]
Then let $w\in H^1(K)/\mathbb R$ be the solution of 
\[
\begin{cases}
-\Delta w= \div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\quad\textrm{ in } K, \\
\;\;\partial_nw=0\qquad\qquad\quad\;\;\,\textrm{ on } \partial K.
\end{cases}
\]
The weak formulation is
\[
(\nabla w, \nabla v)_K=(\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1), v)_K\quad\forall~v\in H^1(K)/\mathbb R.
\]
Obviously we have
\[
\|\nabla w\|_{0,K}\lesssim h_K\|\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\]
Let $I_K^{\div}: \boldsymbol{H}_0(\div,K)\to\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$ be the $L^2$-bounded commuting projection operator in \cite{ChristiansenWinther2008}. Set $\boldsymbol{\phi}_2=-I_K^{\div}(\nabla w)\in\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)$. We have
\begin{equation}\label{eq:20220324-6}
\div\boldsymbol{\phi}_2=-\Delta w=\div(\boldsymbol{\phi}-\boldsymbol{\phi}_1),
\end{equation}
\begin{equation}\label{eq:20220324-7}
\|\boldsymbol{\phi}_2\|_{0,K}\lesssim \|\nabla w\|_{0,K}\lesssim h_K\|\div\boldsymbol{\phi}\|_{0,K} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{equation}
By \eqref{eq:20220324-6}, $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K)\cap\ker(\div)$, which together the exactness of complex \eqref{eq:localBDMfemderhamcomplex0} indicates $\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)$. Hence
\begin{align*}  
\|\boldsymbol{\phi}\|_{0,K}&\lesssim \|\boldsymbol{\phi}_1\|_{0,K}+\|\boldsymbol{\phi}_2\|_{0,K}+\|\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2\|_{0,K} \\
&\lesssim \|\boldsymbol{\phi}_1\|_{0,K}+\|\boldsymbol{\phi}_2\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}-\boldsymbol{\phi}_1-\boldsymbol{\phi}_2, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} \\
&\lesssim \|\boldsymbol{\phi}_1\|_{0,K}+\|\boldsymbol{\phi}_2\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}}.
\end{align*}
Finally \eqref{eq:Vkm1divnormequivalence} holds from \eqref{eq:20220324-5} and \eqref{eq:20220324-7}.
\end{proof}

>>>>

\subsection{Notation}
Let $\Omega\subset \mathbb{R}^d$ be a bounded
polytope. Given a bounded domain $K\subset\mathbb{R}^{d}$ and a
non-negative integer $m$, let $H^m(K)$ be the usual Sobolev space of functions
on $K$.
The corresponding norm and semi-norm are denoted respectively by
$\Vert\cdot\Vert_{m,K}$ and $|\cdot|_{m,K}$. By convention, let $L^2(K)=H^0(K)$. Denote by $L_0^2(K)$ the space of all functions in $L^2(K)$ with zero integral.
Let $(\cdot, \cdot)_K$ be the standard inner product on $L^2(K)$. If $K$ is $\Omega$, we abbreviate
$\Vert\cdot\Vert_{m,K}$, $|\cdot|_{m,K}$ and $(\cdot, \cdot)_K$ by $\Vert\cdot\Vert_{m}$, $|\cdot|_{m}$ and $(\cdot, \cdot)$,
respectively. Let $H_0^m(K)$ be the closure of $\mathcal C_{0}^{\infty}(K)$ with
respect to the norm $\Vert\cdot\Vert_{m,K}$, and $L_0^2(K)$ consist of all functions in $L^2(K)$ with zero mean value.
For integer $k\geq0$,
notation $\mathbb P_k(K)$ stands for the set of all
polynomials over $K$ with the total degree no more than $k$. Set $\mathbb P_{-1}(K)=\{0\}$.
For a banach space $B(K)$, let $B(K; \mathbb{X}):=B(K)\otimes\mathbb{X}$ with $\mathbb{X}=\mathbb{R}^d$ and $\mathbb{K}$, where $\mathbb{K}$ is the set of antisymmetric matrices.
Denote by $Q_k^{K}$ the $L^2$-orthogonal projector onto $\mathbb P_k(K)$ or $\mathbb P_{k}(K; \mathbb{X})$.
For tensor $\boldsymbol{\tau}$, let $\skw\boldsymbol{\tau}:=(\boldsymbol{\tau}-\boldsymbol{\tau}^{\intercal})/2$ be the antisymmetric part of $\boldsymbol{\tau}$.
Denote by $\#S$ the number of elements in a finite set $S$.

@@

In this section we will construct $H(\div)$-conforming macro finite elements in arbitrary dimension.
\subsection{$H(\div)$-conforming finite elements}
For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
\[
\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
\]
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x} \label{BDMdof3}
\end{align}
for $T\in\mathcal T_K$. Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$.
Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.

@@

\begin{lemma}\label{lem:Vkm1divnormequivalence}
For $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
\begin{equation}\label{eq:Vkm1divnormequivalence}
\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{equation}
\end{lemma}
\begin{proof}
\XH{By the inverse inequality \cite{Ciarlet1978,Verfuerth2013} (see also \cite[Lemma 10]{Huang2020}),
$$
h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim  \|\div\boldsymbol{\phi}\|_{-1,K},
$$ 
where
$$
\|\div\boldsymbol{\phi}\|_{-1,K}=\sup_{v\in H_0^1(K)}\frac{(\div\boldsymbol{\phi}, v)_K}{|v|_{1,K}}=-\sup_{v\in H_0^1(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{|v|_{1,K}} \leq \|\boldsymbol{\phi}\|_{0,K}.
$$
Then we have
\begin{equation}\label{eq:20230201}  
h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
\end{equation}
For $F\in\mathcal F^{\partial}(\mathcal T_K)$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$, then apply the trace inequality \cite[Theorem 1.5.1.10]{Grisvard1985} (see also \cite[(2.18)]{BrennerSung2018}) and the inverse inequality to get
$$
h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \|\boldsymbol{\phi}\|_{0,T}+h_T|\boldsymbol{\phi}|_{1,T}\lesssim \|\boldsymbol{\phi}\|_{0,T}.
$$ 
This means
$$
\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
$$ 
Combining \eqref{eq:20230201}, the Cauchy-Schwarz inequality and the last inequality yields
$$
h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
$$
}
% \begin{align*}
% &\quad h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\\
% &\lesssim \|\div\boldsymbol{\phi}\|_{-1,K} + \|\boldsymbol{\phi}\|_{0,K} \lesssim \|\boldsymbol{\phi}\|_{0,K}.    
% \end{align*}

Next we focus on the proof of the \XH{lower bound}. Again we only prove the case $k\geq2$, whose argument can be applied to case $k=1$. Take $\boldsymbol{\phi}_1\in\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)$ such that $(\boldsymbol{\phi}_1\cdot\boldsymbol{n})|_{\partial K}=(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{\partial K}$, and \XH{all the DoFs \eqref{BDMdof1}-\eqref{BDMdof3} of $\boldsymbol{\phi}_1$ interior to $K$ equal to zero}. 
\XH{By the norm equivalence on each simplex $T$ and the vanishing DoFs \eqref{BDMdof2}-\eqref{BDMdof3}, we get
\begin{align}\label{eq:20220324-5}
\|\boldsymbol{\phi}_1\|_{0,K}^2 = \sum_{T\in\mathcal T_K}\|\boldsymbol{\phi}_1\|_{0,T}^2 \eqsim \sum_{T\in\mathcal T_K}\sum_{F\in\mathcal F(T)}h_F\|\boldsymbol{\phi}_1\cdot\boldsymbol{n}\|_{0,F}^2 =\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2.
\end{align}
Due to the vanishing DoF \eqref{BDMdof2}, it holds that $\div\boldsymbol{\phi}_1=Q_0^T(\div\boldsymbol{\phi}_1)$ for $T\in\mathcal T_K$.
% We have
% \begin{equation}
% \|\boldsymbol{\phi}_1\|_{0,K}\eqsim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F},
% \end{equation}
Then apply the integration by parts and the Cauchy-Schwarz inequality to acquire
\begin{equation}\label{eq:202302011}
\|\div\boldsymbol{\phi}_1\|_{0,T}^2=\|Q_0^T(\div\boldsymbol{\phi}_1)\|_{0,T}^2
\leq\frac{1}{|T|}\sum_{F\in\mathcal F(T)\cap\mathcal F^{\partial}(\mathcal T_K)}|F|\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}^2\;\;\forall~T\in\mathcal T_K.
\end{equation}
}
% for $T\in\mathcal T_K$.
Now let $w\in H^1(K)/\mathbb R$ be the solution of 
\[
\begin{cases}
-\Delta w= \div(\boldsymbol{\phi}-\boldsymbol{\phi}_1)\quad\textrm{ in } K, \\
\;\;\partial_nw=0\qquad\qquad\quad\;\;\,\textrm{ on } \partial K.
\end{cases}
\]
The weak formulation is
\[
